spatial_figures

### 2024-10-08 fourmile_outputs_2013edits.Rmd
hru updates

#get rid of a bunch of data
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

@@

############################
### look at month
#get rid of a bunch of data
hru_grid_tmean_jan <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

@@

@@

@@

precip_hrus_jan <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(1,2,3)) %>% 
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

@@

rh_jan <- ggplot() +
  geom_sf(data = hrus_map_rh_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3, 10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

@@

rh_apr <- ggplot() +
  geom_sf(data = hrus_map_rh_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3, 10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

@@

rh_jul <- ggplot() +
  geom_sf(data = hrus_map_rh_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3,10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

##
hru_grid_rh_sep <- hru_grids %>%
  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,10)) %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh_sep <- hru_statn %>%
  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,10)) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

@@

rh_sep <- ggplot() +
  geom_sf(data = hrus_map_rh_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3,10)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

@@

rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
  mutate(RD1_mm_year = (max_rd1_summed/group_area)*1000)

@@

rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
  mutate(rd2_mm_year = (max_rd2_summed/group_area)*1000)

@@

rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
  mutate(rg1_mm_year = (max_rg1_summed/group_area)*1000)

@@

rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
  mutate(rg2_mm_year = (max_rg2_summed/group_area)*1000)

>>>>

```{r}
#get rid of a bunch of data
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

@@

### Tmean season

- Dec-Mar: Winter
- Apr-Jun: Snowmelt/spring
- Jul-Aug: Monsoon
- Sep-Nov: Baseflow/fall

```{r}
############################
### look at month
#get rid of a bunch of data
hru_grid_tmean_jan <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

@@

### Tmax season

- Dec-Mar: Winter
- Apr-Jun: Snowmelt/spring
- Jul-Aug: Monsoon
- Sep-Nov: Baseflow/fall

```{r}
############################
### look at month
#get rid of a bunch of data
hru_grid_tmax_jan <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax_jan <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus_jan <- left_join(hru_grid_tmax_jan, hru_statn_tmax_jan, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax_jan <- left_join(hrus, tmax_hrus_jan, by = 'value')

tmax_jan <- ggplot() +
  geom_sf(data = hrus_map_tmax_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
                       limits = c(-5.1, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

#tmax_jan

## 
hru_grid_tmax_apr <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax_apr <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus_apr <- left_join(hru_grid_tmax_apr, hru_statn_tmax_apr, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')

tmax_apr <- ggplot() +
  geom_sf(data = hrus_map_tmax_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
                       limits = c(-5.1, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

#tmax_apr

#### 
hru_grid_tmax_jul <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax_jul <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus_jul <- left_join(hru_grid_tmax_jul, hru_statn_tmax_jul, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax_jul <- left_join(hrus, tmax_hrus_jul, by = 'value')

tmax_jul <- ggplot() +
  geom_sf(data = hrus_map_tmax_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
                            limits = c(-5.1, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

#tmax_jul

hru_grid_tmax_sep <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax_sep <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus_sep <- left_join(hru_grid_tmax_sep, hru_statn_tmax_sep, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax_sep <- left_join(hrus, tmax_hrus_sep, by = 'value')

tmax_sep <- ggplot() +
  geom_sf(data = hrus_map_tmax_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
                       limits = c(-5.1, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

#tmax_sep
###

lots <- ggarrange(tmax_jan,
                  tmax_apr,
                  tmax_jul,
                  tmax_sep) 
          #nrow = 4)
          #ncol= 0)
lots

@@

### Tmin season

- Dec-Mar: Winter
- Apr-Jun: Snowmelt/spring
- Jul-Aug: Monsoon
- Sep-Nov: Baseflow/fall

```{r}
############################
### look at month
#get rid of a bunch of data
hru_grid_tmin_jan <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin_jan <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus_jan <- left_join(hru_grid_tmin_jan, hru_statn_tmin_jan, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin_jan <- left_join(hrus, tmin_hrus_jan, by = 'value')

tmin_jan <- ggplot() +
  geom_sf(data = hrus_map_tmin_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
                       limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

#tmin_jan

## 
hru_grid_tmin_apr <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin_apr <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(4,5,6)) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus_apr <- left_join(hru_grid_tmin_apr, hru_statn_tmin_apr, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')

tmin_apr <- ggplot() +
  geom_sf(data = hrus_map_tmin_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
                       limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

#tmin_apr

#### 
hru_grid_tmin_jul <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin_jul <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(7,8)) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus_jul <- left_join(hru_grid_tmin_jul, hru_statn_tmin_jul, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin_jul <- left_join(hrus, tmin_hrus_jul, by = 'value')

tmin_jul <- ggplot() +
  geom_sf(data = hrus_map_tmin_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
                            limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

#tmin_jul

hru_grid_tmin_sep <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin_sep <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus_sep <- left_join(hru_grid_tmin_sep, hru_statn_tmin_sep, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin_sep <- left_join(hrus, tmin_hrus_sep, by = 'value')

tmin_sep <- ggplot() +
  geom_sf(data = hrus_map_tmin_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
                       limits = c(-5, 3)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

#tmin_sep
###

lots <- ggarrange(tmin_jan,
                  tmin_apr,
                  tmin_jul,
                  tmin_sep) 
          #nrow = 4)
          #ncol= 0)
lots

@@

precip_hrus_jan <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(12,1,2,3)) %>% 
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

@@

rh_jan <- ggplot() +
  geom_sf(data = hrus_map_rh_jan, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3, 10.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Winter')

@@

rh_apr <- ggplot() +
  geom_sf(data = hrus_map_rh_apr, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3, 10.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Snowmelt')

@@

rh_jul <- ggplot() +
  geom_sf(data = hrus_map_rh_jul, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3,10.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Monsoon')

##
hru_grid_rh_sep <- hru_grids %>%
  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh_sep <- hru_statn %>%
  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
  mutate(month = month(time)) %>%
  filter(month %in% c(9,10,11)) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

@@

rh_sep <- ggplot() +
  geom_sf(data = hrus_map_rh_sep, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
                       limits = c(-3,10.5)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  ggtitle('Fall')

@@

rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
  mutate(RD1_mm_year = ((max_rd1_summed/1000)/group_area)/1000)

@@

rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
  mutate(rd2_mm_year = ((max_rd2_summed/1000)/group_area)/1000)

@@

rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
  mutate(rg1_mm_year = ((max_rg1_summed/1000)/group_area)/1000)

@@

rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
  mutate(rg2_mm_year = ((max_rg2_summed/1000)/group_area)/1000)

### 2024-10-08 spatial_figs.Rmd
hru updates

library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(sf)
library(mapview)
library(raster)
library(sf)
library(terra)
library(viridis)

@@

# update the HRUs
hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
plot(hru_new)

hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')

mapview(hru_new) + mapview(hru_test)
mapview(hru_test)

@@

terrain

@@

```{r}
grid <- read_csv("/Users/megansears/Documents/ages-data-fourmile_creek/output/4milecreek38HRUs-gridallNA_#1/out/Catchment.csv",
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'grid')

statn <- read_csv('/Users/megansears/Documents/ages-data-fourmile_creek/output/4milecreek38HRUs-statnall_na_#1/out/Catchment.csv',
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'statn')

@@

quad <- ggarrange(p_cols, 
          t_moplot,
          sol_moplot,
          rh_moplot,
          common.legend = T,
          legend = 'bottom',
          ncol=4) 
          #nrow = 4)
          #ncol= 0)
quad

@@

@@

rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)") +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

@@

sr <- ggplot() +
  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")")) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  guides(
    fill = guide_colorbar(
      label.theme = element_text(size = 10)))

@@

precip <- ggplot() +
  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)") +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

@@

tmean <- ggplot() +
  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

@@

tmin <- ggplot() +
  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmin difference (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

@@

tmax <- ggplot() +
  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmax difference (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=13.5) +
  theme_void() +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

lots <- ggarrange(precip,
                  sr,
                  rh,
                  tmean,
                  tmax,
                  tmin) 
          #nrow = 4)
          #ncol= 0)
lots

ggsave("./figures/diff.png", plot = lots, dpi = 600)

@@

ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year))) + 
  geom_line(size = 1.1) +
  theme_bw(base_size = 20) +
  labs(y = 'Discharge (cms)', color = 'Year') +
  scale_color_viridis_d(option = "turbo")

>>>>

library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(sf)
library(mapview)
library(raster)
library(sf)
library(terra)
library(viridis)
library(ggpubr)

@@

# update the HRUs
hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
plot(hru_new)

hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')

mapview(hru_new) 
#mapview(hru_test)

@@

terrain
ggsave('./figures/fig1a.png', dpi=600)
##

reference_location <- data.frame(
  x = -105.2705,  # Longitude for Boulder
  y = 40.0150,    # Latitude for Boulder
  name = "Boulder, CO"
)

# Your existing terrain plot
terrain2 <- ggplot() +
  geom_raster(data = dem_df, 
              aes(x = x, y = y, fill = layer)) +  
  scale_fill_gradientn(colors = terrain.colors(200),  
                       name = "Elevation (m)") +
  geom_sf(data = fire, 
          aes(color = "Fire"), 
          fill = NA, 
          lwd = 0.75) +
  geom_sf(data = hru_new, 
          aes(color = "HRU"), 
          fill = NA, 
          lwd = 0.5) +
  geom_sf(data = locations, 
          aes(shape = factor(display_use)), 
          size = 4) + 
  scale_shape_manual(values = custom_shapes) +
  scale_color_manual(name = NULL,
                     values = c(Fire = "red", HRU = "black"), 
                     labels = c(Fire = "Fourmile Canyon fire", HRU = "HRUs")) + 
  labs(shape = element_blank()) +
  theme_bw(base_size = 25) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.spacing.y = unit(0.01, "cm")) +
  geom_point(data = reference_location, aes(x = x, y = y), color = "blue", size = 4, shape = 21, fill = "yellow") + # Reference marker
  geom_text(data = reference_location, aes(x = x, y = y, label = name), vjust = -1, color = "blue") # Reference label

terrain2
``##

@@

```{r}
grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'grid')

statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'statn')

@@

quad <- ggarrange(p_cols, 
          t_moplot,
          sol_moplot,
          rh_moplot,
          common.legend = T,
          legend = 'bottom',
          ncol=2,
          nrow=2) 
          #nrow = 4)
          #ncol= 0)
quad

@@

quad_plus <- ggarrange(flow_plot,quad,
                       nrow=2)
quad_plus

ggsave("./figures/quad_plus.png", plot = quad_plus, dpi = 600)

@@

####
rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

@@

sr <- ggplot() +
  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

@@

precip <- ggplot() +
  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

@@

tmean <- ggplot() +
  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

@@

tmin <- ggplot() +
  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmin (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

@@

tmax <- ggplot() +
  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmax (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

tmax

bottom_theme <-   theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    legend.key.width = unit(.75, "cm"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = unit(c(-6, 0, 0, 0), "cm"), 
    panel.spacing = unit(0, "lines"))

top_theme <-   theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    legend.key.width = unit(.75, "cm"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = unit(c(0, 0, -6, 0), "cm"), 
    panel.spacing = unit(0, "lines"))

lots <- ggarrange(
  precip, sr, rh, tmean, tmax, tmin,
  heights=)

lots

ggsave("./figures/diff_update.png", plot = lots, dpi = 600)

@@

flow_plot <- ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year))) + 
  geom_line(size = 1.1) +
  theme_bw(base_size = 20) +
  labs(y = 'Discharge (cms)', color = 'Year') +
  scale_color_viridis_d(option = "turbo")

flow_plot
